refnx -- Neutron and X-ray reflectometry analysis in Python

### 2018-07-26 paper/manuscript.tex
PAPER: pdf images

The parameters used in the \LipidLeaflet\ component are: area per molecule ($A$), thicknesses for each of the head and tail regions ($t_x$), sums of scattering lengths of the head and tail regions ($b_x$), partial volumes of the head and tail groups ($V_x$), roughness between head and tail region, and SLDs of the solvents for the head and tail group ($\rho_{x,\mathrm{solv}}$). The overall SLD of each of the head and tail group regions are given by:
%TODO cite a paper which gives a whole load of volumes?
\begin{gather} 
\label{eqn:3} \phi_{x} = \frac{V_x}{At_x}\\
\rho_x =  \phi_{x} \frac{b_x}{V_x} + (1 - \phi_{x})\rho_{x,\mathrm{solv}} \label{eqn:4}
\end{gather}
The approach used in \LipidLeaflet\ component ensures that there is a 1:1 correspondence of heads to tails.
By default the head and tail solvents are assumed to be the same as the solvent that is used throughout the \Structure. This will be the case when using \LipidLeaflet\ for a solid-liquid reflectometry experiment. However, at the air-liquid, or liquid-liquid interfaces the solvent for the head and tail region may be different, and it is possible to use different solvent SLDs for each. We note that the \LipidLeaflet\ component may also be used to describe other amphiphiles adsorbing at an interface.

@@

\begin{figure}%
\centering
\label{fig:global_fit}%
\includegraphics[width=85mm]{./supporting_information/global_fit.png}%
%TODO: series labels on plots; delete points?;
%TODO: artefact in high q d2o fit; truncate at Q = 0/35 ?
%TODO: h2o fit isn't great about 0.20

\includegraphics[width=85mm]{./supporting_information/d2o_sld_spread.png}

@@

\begin{figure}
  \includegraphics[width=175mm]{./supporting_information/corner.png}
  \caption{Corner plot for the varying parameters of DMPC bilayers measured at three contrasts. The sampling took $\sim$13 minutes on a \SI{3.2}{GHz} quad-core computer for 30 saved steps, corresponding to 6000 samples, with the steps being thinned by a factor of 100. A larger scale image is available in supporting information.}
  \label{fig:corner}
\end{figure}

@@

\noindent
\textbf{gui.ipynb} - \Jupyter\ notebook used to create the GUI screenshot.\\
\textbf{lipid.ipynb} - \Jupyter\ notebook used for the lipid analysis example.\\
\textbf{lipid.pdf} - PDF view of the \Jupyter\ notebook used for the lipid analysis example.\\
\textbf{corner.pdf} - larger scale image of the corner plot.\\
\textbf{c_PLP0016596.dat}, \textbf{c_PLP0016601.dat}, \textbf{c_PLP0016607.dat} - example lipid datasets.\\
\textbf{reduction.ipynb} - notebook for reducing example datasets.\\
\textbf{raw_data.zip} - raw files for the example datasets.\\
\textbf{refnx-paper.yml} - \conda\ environment file to reproduce the analysis environment in this paper.

>>>>

The parameters used in the \LipidLeaflet\ component are: area per molecule ($A$), thicknesses for each of the head and tail regions ($t_x$), sums of scattering lengths of the head and tail regions ($b_x$), partial volumes of the head and tail groups ($V_x$), roughness between head and tail region, and SLDs of the solvents for the head and tail group ($\rho_{x,\mathrm{solv}}$). The overall SLD of each of the head and tail group regions are given by:

\begin{gather} 
\label{eqn:3} \phi_{x} = \frac{V_x}{At_x}\\
\rho_x =  \phi_{x} \frac{b_x}{V_x} + (1 - \phi_{x})\rho_{x,\mathrm{solv}} \label{eqn:4}
\end{gather}
The approach used in \LipidLeaflet\ component ensures that there is a 1:1 correspondence of heads to tails.
By default the head and tail solvents are assumed to be the same as the solvent that is used throughout the \Structure. This will be the case when using \LipidLeaflet\ for a solid-liquid reflectometry experiment. However, at the air-liquid, or liquid-liquid interfaces the solvent for the head and tail region may be different, and it is possible to use different solvent SLDs for each. We note that the \LipidLeaflet\ component may also be used to describe other amphiphiles adsorbing at an interface.

@@

\begin{figure}%
\centering
\label{fig:global_fit}%
\includegraphics[width=85mm]{./supporting_information/global_fit.pdf}%
%TODO: series labels on plots; delete points?;
%TODO: artefact in high q d2o fit; truncate at Q = 0/35 ?
%TODO: h2o fit isn't great about 0.20

\includegraphics[width=85mm]{./supporting_information/d2o_sld_spread.pdf}

@@

\begin{figure}
  \includegraphics[width=175mm]{./supporting_information/corner.pdf}
  \caption{Corner plot for the varying parameters of DMPC bilayers measured at three contrasts. The sampling took $\sim$13 minutes on a \SI{3.2}{GHz} quad-core computer for 30 saved steps, corresponding to 6000 samples, with the steps being thinned by a factor of 100. A larger scale image is available in supporting information.}
  \label{fig:corner}
\end{figure}

@@

\noindent
\textbf{gui.ipynb} - \Jupyter\ notebook used to create the GUI screenshot.\\
\textbf{lipid.ipynb} - \Jupyter\ notebook used for the lipid analysis example.\\
\textbf{lipid.pdf} - PDF view of the \Jupyter\ notebook used for the lipid analysis example.\\
\textbf{corner.pdf} - larger scale image of the corner plot.\\
\textbf{c\_PLP0016596.dat}, \textbf{c\_PLP0016601.dat}, \textbf{c\_PLP0016607.dat} - example lipid datasets.\\
\textbf{reduction.ipynb} - notebook for reducing example datasets.\\
\textbf{raw\_data.zip} - raw files for the example datasets.\\
\textbf{refnx-paper.yml} - \conda\ environment file to reproduce the analysis environment in this paper.
